{Formal Verification of Rust Programs with Creusot}\\{\large CS 6110 Software Verification Final Project

### 2023-05-09 paper.tex
Final section, tighten up formatting

\documentclass[12pt]{article}
\usepackage{graphicx} % Required for inserting images
\usepackage{biblatex}
\usepackage{hyperref}
\usepackage{fullpage}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{amsmath}
\usepackage{amsfonts}

@@

\title{CS6110: Software Verification Final Project: Formal Verification of Rust Programs with Creusot}
\author{Taylor Allred \texttt{taylor.allred21@gmail.com}\\ Ashton Wiersdorf \texttt{research@wiersdorfmail.net}}
\date{Spring 2023}

@@

\maketitle

@@

\clearpage
\pagenumbering{arabic}
\section{Overview of Creusot}

@@

Creusot works by installing a helper tool to run with Rust's \texttt{cargo} build and package manager.

@@

@@

@@

% Local Variables:
% jinx-local-words: "CreuSAT Creusot's Kani Pearlite WhyML creusot"
% End:

>>>>

\documentclass[12pt]{article}
\usepackage{graphicx} % Required for inserting images
\usepackage{biblatex}
\usepackage{hyperref}
\usepackage{fullpage}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{geometry}

@@

\title{{Formal Verification of Rust Programs with Creusot}\\{\large CS 6110 Software Verification Final Project}}
\author{Taylor Allred \texttt{taylor.allred21@gmail.com}\\ Ashton Wiersdorf \texttt{research@wiersdorfmail.net}}
\date{Spring 2023}

@@

\newgeometry{top=0.5in}
\maketitle

@@

\clearpage
\restoregeometry
\pagenumbering{arabic}
\section{Overview of Creusot}

@@

Creusot works by installing a helper tool to run with Rust's \texttt{cargo} build and package manager.
One adds the the Creusot annotations to rust code, runs \texttt{cargo creusot}, and then opens the \texttt{.mlcfg}\footnote{\texttt{.mlcfg} is an alternate to the WhyML input format.} in Why3, and works on verifying the code.
One can also simply run \texttt{cargo build} to compile the Rust program---all Creusot annotations will be elided and the program will compile like normal Rust code.

@@

\subsection{Running the example}

Unfortunately, despite our best efforts, we were not able to make Creusot run top-to-bottom.
All the documentation was too out of date, and the toolchain was too unstable.
The most we were able to do was verify CreuSAT---Creusot \emph{can} work---but we were unable to make it work on even simple examples.

@@

\subsection{What we gained}

We considered exposure to Why3 and more experience with how Rust's linear type system enables static analysis to be the two most valuable parts of this research.
Why3 is a versatile platform that enjoys an impressive amount of stability and functionality.
Rust's linear type system continues to deliver---not only does it make reasoning about memory tractable for a compiler, at also makes verifying code so much simpler than with C or C++ where naked pointers with undecidable lifetimes abound.

@@

% Local Variables:
% jinx-local-words: "CreuSAT Creusot's Kani Pearlite Qed WhyML creusot forall mlcfg"
% End:
